Figure supplements

### 2023-05-06 Manuscript/Manuscript.Rmd
upload ms in Manuscript/

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: "*Kei Jokura, Nobuo Ueda, Martin Gühmann, Luis Alfonso Yañez-Guerra, Piotr Słowiński, Kyle C. A. Wedgwood, Gáspár Jékely*"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4
  4QD, UK*"
output:
  pdf_document:
    latex_engine: lualatex
    template: default
  html_document:
    theme: lumen
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

![**Figure 1. Identification of NOS-expressing interneurons (INNOS) within the cPRC circuit.** **(A)** SEM image of a three-day-old Platynereis larva. **(B, C)** Five types of neurons (cPRC, INNOS, INRGW, Ser-h1 and MC) in the cPRC circuit reconstructed in the whole-body transmission electron microscopy (ssTEM) dataset of a three-day-old larva. Ciliated cells labelled with (B) are shown in grey. The INNOS on the ventral side labelled with (C) are shown in purple. Axons and dendrites appear as lines and cell body positions are represented by spheres. **(D)** Expression analysis of the NOS gene (magenta) using in situ HCR. Anterior view of the larva at two-day-old. Co-stained image using acetylated α-tubulin antibody (acTub: green). **(E)** Immunostaining with anti-HA antibody against HA tagged palmitoylated-tdTomato expressed under the upstream of the start site of NOS (NOSp::palmi-3xHA: magenta). Co-staining with acetylated α-tubulin antibody as marker for cilia of cPRC and axonal scaffold (acTub: green). Views of larvae at three-day-old from the anterior side. Insert: One of the reconstracted INNOS is shown from the anterior side. **(F)** Wiring diagram of the cPRC circuit. Hexagons and arrows represent cell groups and their synaptic connections, respectively. Numbers inside hexagons indicate the number of cells grouped in each node. Arrow line thickness (synapse weight) is equal to the number of synapses.](../figures/Fig1.png){width="100%"}

@@

![**Figure 5. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** **(A, B)** Each left figure shows a calcium imaging using GCaMP6s. The respective right figures show immunostaining images of the same positions in the respective left figures, (A) shows RYamide antibodies, (B) shows RGWamide and serotonin (5-HT) antibodies in red and DAPI in cyan. Asterisks indicate the nuclei of the cPRC, respectively, and the nuclei of the cells that were identified from the arrangement of the surrounding cells are indicated by numbers. From the position of the cells, the calcium imaging data identify INNOS in (A) and INRGW and Ser-h1 in (B), respectively. **(C)** Correlation (Pearson's r) map of neuronal activity of the INNOS, INRGW, Ser-h1 and MC neurons. **(D)** Changes over time in GCaMP6s intensities in INNOS when cPRC is stimulated with UV in WT (dark purple) and NOSΔ11/Δ11 mutant (light purple) larvae. **(E)** Changes over time in GCaMP6s intensities in INNOS when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: pink and light pink) larvae. **(F)** Changes over time in GCaMP6s intensities in INRGW when cPRC is stimulated with UV in WT (dark blue) and NOSΔ23/Δ23 mutant (light blue) larvae. **(G)** Changes over time in GCaMP6s intensities in INRGW when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: blue and light blue). **(H, I)** Changes over time in GCaMP6s intensities in Ser-h1 and MC when cPRC is stimulated with UV in WT (Ser-h1 and MC: dark red and brown) and NOSΔ11/Δ11 mutant (Ser-h1 and MC: light red and brown) larvae.](../figures/Fig5.png){width="100%"}

>>>>

---
title: Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance
  in zooplankton
author: 
  - name: "Luis Alberto Bezares Calderón<sup>1,`*`</sup>, Réza Shahidi<sup>1,2</sup> and Gáspár Jékely<sup>1,3,`*`</sup>"
    affiliation: "<sup>1</sup>Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 <br> <sup>2</sup>Electron Microscopy Core Facility (EMCF), University of Heidelberg, 69120 Heidelberg, Germany <br> <sup>3</sup>Centre for Organismal Studies (COS), University of Heidelberg, 69120 Heidelberg, Germany  <br> <sup>*</sup>Correspondence`:` l.a.bezares-calderon @ exeter.ac.uk, gaspar.jekely @ cos.uni-heidelberg.de"
output:
  html_document:
    theme: lumen
  pdf_document:
    latex_engine: lualatex
    template: default
  word_document: default
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
monofont: Times New Roman
documentclass: article
classoption: onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

```{r echo=FALSE,fig.cap="**Figure 1. Identification of NOS-expressing interneurons (INNOS) within the cPRC circuit.** **(A)** SEM image of a three-day-old Platynereis larva. **(B, C)** Five types of neurons (cPRC, INNOS, INRGW, Ser-h1 and MC) in the cPRC circuit reconstructed in the whole-body transmission electron microscopy (ssTEM) dataset of a three-day-old larva. Ciliated cells labelled with (B) are shown in grey. The INNOS on the ventral side labelled with (C) are shown in purple. Axons and dendrites appear as lines and cell body positions are represented by spheres. **(D)** Expression analysis of the NOS gene (magenta) using in situ HCR. Anterior view of the larva at two-day-old. Co-stained image using acetylated α-tubulin antibody (acTub: green). **(E)** Immunostaining with anti-HA antibody against HA tagged palmitoylated-tdTomato expressed under the upstream of the start site of NOS (NOSp::palmi-3xHA: magenta). Co-staining with acetylated α-tubulin antibody as marker for cilia of cPRC and axonal scaffold (acTub: green). Views of larvae at three-day-old from the anterior side. Insert: One of the reconstructed INNOS is shown from the anterior side. **(F)** Wiring diagram of the cPRC circuit. Hexagons and arrows represent cell groups and their synaptic connections, respectively. Numbers inside hexagons indicate the number of cells grouped in each node. Arrow line thickness (synapse weight) is equal to the number of synapses."}

knitr::include_graphics(path = "Manuscript/figures/Fig1.png")

@@

![**Figure 5. NO produced by UV stimulation to cPRCs induces a depolarising response in cPRC via NIT-GC1.** **(A, B)** Each left figure shows a calcium imaging using GCaMP6s. The respective right figures show immunostaining images of the same positions in the respective left figures, (A) shows RYamide antibodies, (B) shows RGWamide and serotonin (5-HT) antibodies in red and DAPI in cyan. Asterisks indicate the nuclei of the cPRC, respectively, and the nuclei of the cells that were identified from the arrangement of the surrounding cells are indicated by numbers. From the position of the cells, the calcium imaging data identify INNOS in (A) and INRGW and Ser-h1 in (B), respectively. **(C)** Correlation (Pearson's r) map of neuronal activity of the INNOS, INRGW, Ser-h1 and MC neurons. **(D)** Changes over time in GCaMP6s intensities in INNOS when cPRC is stimulated with UV in WT (dark purple) and NOSΔ11/Δ11 mutant (light purple) larvae. **(E)** Changes over time in GCaMP6s intensities in INNOS when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: pink and light pink) larvae. **(F)** Changes over time in GCaMP6s intensities in INRGW when cPRC is stimulated with UV in WT (dark blue) and NOSΔ23/Δ23 mutant (light blue) larvae. **(G)** Changes over time in GCaMP6s intensities in INRGW when cPRC is stimulated with UV in NIT-GC2 morphants (MO1 and MO2: blue and light blue). **(H, I)** Changes over time in GCaMP6s intensities in Ser-h1 and MC when cPRC is stimulated with UV in WT (Ser-h1 and MC: dark red and brown) and NOSΔ11/Δ11 mutant (Ser-h1 and MC: light red and brown) larvae.](Manuscript/figures/Fig5.png){width="100%"}

### 2023-05-06 Manuscript/Supplements.Rmd
upload ms in Manuscript/

![**Figure 1---figure supplement 2.** Expression analysis of the NOS gene (magenta) using in situ HCR using the larva at 3-day-old in dorsal view (A) and anterior view (B). (B) Insert: showing two NOS cells on each side.](../figures/Fig1_sup2.png){width="100%"}

![**Figure 3---figure supplement 1.** **(A)** Overlaid trajectories for WT (left, n=20) and NOS mutant (right, n=31) 2-day-old larvae. Grey shows the trajectories before UV stimulation and purple shows the trajectories after UV stimulation. **(B)** The temporal changes in the vertical position of the WT and mutant 2-days-old larvae before and after UV stimulation are shown. The starting points of each larval trajectory are set to 0. After UV stimulation is indicated by purple squares. **(C)** Vertical swimming in wild-type (WT) and mutant (NOSΔ11 and NOSΔ23) larvae at 2-day-old stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. **(D, E)** The temporal changes in the distance traveled of the WT and mutant in 2-day (D) and 3-day-old (E) larvae before and after UV stimulation are shown.](../figures/Fig3_sup1.png){width="100%"}

@@

![**Figure 4---figure supplement 2.** **(A)** Co-expression analysis image of the NIT-GC1 (magenta) and MLD-pedal2 amide proneuropeptide gene (MLD: green). Anterior view of the larva at 2-day-old. **(B, C)** Expression analysis of the NIT-GC2 gene (magenta) using in situ HCR. Anterior (B) and posterior (C) views of the larva at 3-day-old. **(D, E)** Localisation analysis for NIT-GC1 (B) and NIT-GC2 (C) morphant using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (acTub). Anterior view of the larva at 2-day-old. **(F)** Co-localisation analysis using NIT-GC1 (magenta) and NOS (green) antibodies. Anterior view of the larva at 2-day-old.](../figures/Fig4_sup2.png){width="100%"}

>>>>

![**Figure 1---figure supplement 2.** Expression analysis of the *NOS* gene (magenta) using in situ HCR using the larva at three-day-old in dorsal (A) and anterior view (B). (B) Insert: showing two NOS cells (INNOS_dl and INNOS_vl) on left side.](../figures/Fig1_sup2.png){width="100%"}

![**Figure 3---figure supplement 1.** **(A)** Overlaid trajectories for WT (n=37) and NOS mutant (NOSΔ11/Δ11, n=18 and NOSΔ23/Δ23, n=8) at two-day-old larvae. 0 sec as the starting point. After 10 sec, UV (395 nm) stimulation from the side. **(B)** The temporal changes in the vertical position of the WT and mutant 2-days-old larvae before and after UV stimulation are shown. The starting points of each larval trajectory are set to 0. After UV stimulation is indicated by purple squares. **(C)** Vertical swimming in wild-type (WT) and mutant (NOSΔ11 and NOSΔ23) larvae at 2-day-old stimulated with UV (395 nm) light from side, blue (488 nm) light from top and UV (395 nm) light from top. The data are shown in 30 s bins. **(D, E)** The temporal changes in the distance traveled of the WT and mutant in 2-day (D) and 3-day-old (E) larvae before and after UV stimulation are shown.](../figures/Fig3_sup1.png){width="100%"}

@@

![**Figure 4---figure supplement 2.** **(A)** Co-expression analysis image of the NIT-GC1 (magenta) and MLD-pedal2 amide proneuropeptide gene (MLD: green). Anterior view of the larva at two-day-old. **(B, C)** Expression analysis of the NIT-GC2 gene (magenta) using in situ HCR. Anterior (B) and posterior (C) views of the larva at three-day-old. **(D)** Co-localisation analysis using NIT-GC1 (magenta) and NOS (green) antibodies. Anterior view of the larva at two-day-old. **(E, F)** Localisation analysis using NIT-GC1 and NIT-GC2 antibodies for NIT-GC1 (E) and NIT-GC2 (F) morphant. Green shows co-staining with acetylated α-tubulin antibody (acTub). Anterior view of the larva at two-day-old.](../figures/Fig4_sup2.png){width="100%"}

![**Figure 5---figure supplement 1.** Schematic diagram of the immunostaining procedure after calcium imaging.](../figures/Fig5_sup1.png){width="100%"}
